CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-17 paper/ms.tex
Add diagnostic plots 7,8
Add diagnostic figure 2,3,4

\centerline{Fig.1 Histogram of a b c for apstar data (What we use now)}
\bigskip

Plot log g vs teff for all the stars we use in the training step.

@@

\centerline{Fig.2 Log g vs Teff for the training set}
\bigskip

>>>>

\centerline{Diagnostic Fig.1 Histogram of a b c for apstar data (What we use now)}
\bigskip

Comparison of the spectrum if we set the parameters showed in old figure 8. In old figure 8, the red line and the green line are on the top of each other
 \bigskip

@@

\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters showed in old figure 8}
\bigskip

Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
 \bigskip

 Comparison of the spectrum if we set the parameters showed in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
 \bigskip

\includegraphics[width=170mm]{d_figure_3.png}
\bigskip

\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters showed in old figure 9}
\bigskip

Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
 \bigskip

 If we want a plot like old figure 9, we can manually set a=0.5, b=1 and c= -0.5. Here a+b+c is not equal to 1 and this is the cause of the offset.
 \bigskip

\includegraphics[width=170mm]{d_figure_4.png}
\bigskip

\centerline{Diagnostic Fig.4 Comparison of the spectrum if we want a big difference between the red line and the green line}
\bigskip

Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.
 \bigskip
